
# Setup
Do whatever setup you do here, such as loading libraries

```{r setup, message=FALSE}
# Load standard libraries
library("tidyverse")
library("margins")
```


## Question 1.1

# Question 1.1.1
Period life expectancies use mortality rates from a single year (or group of years) and assume that those rates apply throughout the remainder of a person's life. This means that any future changes to mortality rates would not be taken into account.It is a eeasier way to predict life expectancies.
source: office for national statistics, census
https://www.ons.gov.uk/peoplepopulationandcommunity/birthsdeathsandmarriages/lifeexpectancies/methodologies/periodandcohortlifeexpectancyexplained

# Question 1.1.2
After reading the file, I did the data cleaning for this data frame. After cleaning, there are 11618 obs in total.
1. Remove all cases with missing life expectancy, year, and country name or code.
2. Change the country name from "Korea, Republic of" to "South Korea"
```{r}
gapminder<- read.delim("gapminder.csv.bz2")
gapminder <- gapminder %>%
  filter(!is.na(lifeExpectancy), !is.na(time), !is.na(name))%>%
  filter(name!="")%>%
  mutate(name = ifelse(name == "Korea, Republic of", "South Korea", name))
```

# Question 1.1.3
a. 204 countries in the gapminder data frame

b. First year min:1960, Last year max:2019

c. Life expectancy min:18.907, year=1977, Country=Cambodia

 Life expectancy max:85.417, year=2012, Country=San Marino

d. The lowest life expectancy was in Cambodia in 1977.
That is because nearly two million people died under the rule of the fanatical Communist movement, which imposed a ruthless agenda of forced labor, thought control, and mass execution on Cambodia. 

source: https://www.ushmm.org/genocide-prevention/countries/cambodia/cambodia-1975
```{r}
length(unique(gapminder$name))
range(gapminder$time)
head(gapminder[gapminder$time ==1960,])
head(gapminder[gapminder$time==2019,])

range(gapminder$lifeExpectancy)
gapminder[gapminder$lifeExpectancy ==18.90700,]
gapminder[gapminder$lifeExpectancy==85.41707,]
```

# Question 1.1.4
a. I plot all countries in grey and make the selected countries with colors.

b. Except for the selected countries "United States of America", "South Korea", "Cambodia", "China". I also chose "Hong Kong" and "Japan" in my chart because I am familiar with HK and JP and I am interested in how the life expectancy will grow in those two Asia countries.
```{r}
selected_countries <- c("United States of America", "South Korea", "Cambodia", "China", "Hong Kong", "Japan")
selected_country <- gapminder[gapminder$name %in% selected_countries, ]

ggplot() +
  geom_line(data = gapminder, aes(x = time, y = lifeExpectancy, group = name), color = "grey", alpha = 0.5) +
  geom_line(data = selected_country, aes(x = time, y = lifeExpectancy, group = name, color = name)) +
  labs(title = "Life Expectancy - All Countries and Selected Countries",
       x = "Year",
       y = "Life Expectancy",
       color = "Country")


```
# Question 1.1.5
For the grey lines, we can see that the overall life expectancy in all countries have increased gradually with the time. There are many possible factors that may can explain this scenario. Economy development has grow rapidly to achieve longer life, healthy life style has become the trend for recent years and the improvement for the medical industry may be the reasons why life expectancy has increased.

For the colored lines, we can see that most developed countries, including Hong Kong, Japan and US have higher life expectancy compared with other countries and the life expectancy has increased as the time goes. 

On the other hand, South Korea used to have lower life expectancy during 1960-1980, i think this is because of the Korea War that happened in 1950s that caused the economy recession.

China has low life expectancy during 1960s and has gradually increased as their economy has improved during the past thirty years. 

Lastly, Combodia has the lowest life expectancy in 1977.
That is because nearly two million people died under the rule of the fanatical Communist movement, which imposed a ruthless agenda of forced labor, thought control, and mass execution on Cambodia. Even though their life expectancy has increased during the past few years, it is apparent that it is still lower compared to other countries.


# Question 1.1.6
geom_path can allow me to explore how two variables(fertilityRate and lifeExpectancy) are related over time, the arrow shows how the time flows
```{r}

ggplot() +
  geom_path(data = gapminder, aes(x =fertilityRate, y = lifeExpectancy, group = name), color = "grey", alpha = 5, arrow=arrow()) +
  geom_path(data = selected_country, aes(x = fertilityRate, y =lifeExpectancy , group = name, color = name), arrow=arrow()) +
  labs(title = "Life Expectancy vs Fertility Rate",
       x = "Fertility Rate",
       y = "Life Expectancy",
       color = "Country")
```

# Question 1.1.7
According to the chart above, when the the life expectancy is low, the fertility rate is higher, this is usually happening in the early years which the sanitary condition is bad. I think when the health and medical condition is bad, people get sick and die easily, so they havee to make more babies to fulfill the labor market. As the medical condition improved nowadays (like how the arrow shows in the graph), the fertality rate has decreased and the life expectancy has increased.

When it comes to specific countries, Cambodia has a drop in life expectancy because nearly two million people died under the rule of the fanatical Communist movement, which imposed a ruthless agenda of forced labor, thought control, and mass execution on Cambodia.



# Question 1.2.1
The distribution here is left skewed.
No, i don't think it requires log transformation in this scenario.
Log transformation is usually used in price or income, which should be a well-defined lower bound but no obvious upper bound. But in this case, there are both upper and lower bond. After trying to do the log transformation in graph 2, it doesn't become more normal distribution. Therefore,a log transformation is not required.
```{r}
ggplot(gapminder, aes(x = lifeExpectancy)) +
  geom_histogram(binwidth = 2, fill = "skyblue", color = "white") +
  labs(title = "Distribution of Life Expectancy",
       x = "Life Expectancy",
       y = "Frequency") 

#after log
ggplot(gapminder, aes(x = log(lifeExpectancy)))+
  geom_histogram(binwidth = 0.01, fill = "skyblue", color = "white") +
  labs(title = "Distribution of Life Expectancy-log",
       x = "Life Expectancy-log",
       y = "Frequency") 
```

# Question 1.2.2
create a gapminder_model to see how time affects the life expectancy.
 I() function here stands for "as is", which means the year-2000
```{r}
lm(lifeExpectancy ~ time, data = gapminder) #without -2000 in time
lm(lifeExpectancy ~ I(time-2000), data = gapminder)
gapminder_model <- lm(lifeExpectancy ~ I(time-2000), data = gapminder)  #-2000 in time
summary(gapminder_model)
```

# Question 1.2.3
I think that is because we can to decrease the gap between year and life expectancy. 

I tried to do the model without -2000 in time and find that the intercept is -550.
when i do the model  -2000 in time, the intercept became 67.358,which is more readable and easier to do the analysis.

# Question 1.2.4
B0: 67.358
B1: 0.309
The life expectancy is increasing over time because  B1 is positive.
When time increases by one unit, the life expectancy  will increase by 67.358+0.309
The p-value means the possibility of H0 will happen, since p-value is very small(<2e-16), which means the H0 is unlikely to happen. Therefore,that lead us to conclude that we could reject the null hypothesis.

# Question 1.2.5
```{r}
gapminder_model1 <- lm(lifeExpectancy ~ I(time-2000)+region, data = gapminder) #-2000 in time
summary(gapminder_model1)
```
# Question 1.2.6
What do the region dummies mean? >> means there are multi-categories in the region variable, including Africa, Americas, Europe, Asia and Oceania.

What is the reference category? >> Africa is the reference category here.

How big is the time trend? >> Since B1 (0.304745) is positive, that means the life expectancy is increasing over time.

Is it statistically significant? >> All the p-value is very small(<2e-16), which means it is statistical significance because we have the evidence to reject null hypothesis that the time trend is zero.
B0: if regionAmerica, Asia, Europe, Oceania and time  = 0, i.e Ethnicity = “Africa”, then life expectancy is 55.94
B1: if time increases by one unit, regio,nAmerica Asia, Europe, Oceania  = 0, then life expectancy increases by 55.94+0.304
B2: if regionAmerica=1, regionAsia, Europe, Oceania and time  = 0, ”, then life expectancy increases by 55.94+15.87
B3: if regionAsia=1, regionAmerica, Europe, Oceania and time  = 0, ”, then life expectancy increases by 55.94+12.15
B4: if regionEurope=1, regionAsia, Americae, Oceania and time  = 0, ”, then life expectancy increases by 55.94+20.83
B5: if regionOceania=1, regionAsia, Europe, Americaa and time  = 0, ”, then life expectancy increases by 55.94+13.57

Is it different from what you saw in the previous model? >> The conclusion is the same. There is a positive relationship between time and life expectancy. The B0, B1 is slightly different.

# Question 1.2.7
```{r}
gapminder_model2 <- lm(lifeExpectancy ~ I(time-2000)+region+log(GDP_PC)+fertilityRate, data = gapminder) 
summary(gapminder_model2)
```

# Question 1.2.8
log(GDP_PC) here the Beta means if log(GDP_PC) increases by one unit, other variables remain the same, then the life expectancy will increase by 49.936+2.49
fertilityRate here the Beta means if fertilityRate increases by one unit, other variables remain the same, then the life expectancy will decrease by 49.936-2.235

# Question 1.2.9
In 1.2.5, we can see that Europe was the leading region, which means the coefficient is the largest.
In 1.2.7, we can see that America was the leading region, the dummy for Europe is only 4th largest. 

That is because in multi-category dummies, the indirect variables will slightly have cross effect on each other. Since we use different variables in different models, the coefficient in different models may be a little bit different.

# Question 1.2.10
According to the model in Question 1.2.5 and the confirmation below. 
Europe has the highest life expectancy and Africa has the lowest life expectancy.

```{r}
tapply(gapminder$lifeExpectancy, gapminder$region, mean)
```

## Question 2
# Question 2.1
```{r}
italian_cheap<- read.delim("nyc-italian-cheap.csv.bz2")
italian_cheap <- italian_cheap %>%
filter(!is.na(Restaurant), !is.na(Cheap), !is.na(East), !is.na(Food),!is.na(Decor),!is.na(Service))
```

# Question 2.2
Cheap variable is considered cheap(1) and expensive(0), which means its a binary variable. 
Therefore, we should use logistic regression to compute this. In R, we use glm function, the B1 in logistic regression is difficult to interpret, therefore, we use AME to interpret.

# Question 2.3
The B1 here is difficult to interpret, therefore, we use AME to calculate, which answers the similar question as slope B1 in linear. AME means how much likely of cheap would be affected (in average) by other variables. 

We can interpret the results by AME:
Decor: one unit higher in Decor 8.5 pct points less likely to be cheap 

East: restaurant located east of the 5th Ave. is  4.4 pct points less likely to be cheap

Food: one unit higher in Food 6.37 pct points less likely to be cheap 

Service: one unit higher in Service 0.64 pct points more likely to be cheap 
```{r}
m <- glm(Cheap ~ Food+Decor+Service+East, data=italian_cheap, family=binomial())
summary(m)
summary(margins(m))
```

# Question 2.4
Use the model m above to predict the two restaurants.
Assagio Ristorante: prob:0.2358072>>not cheap(close to 0)
Altura: prob:0.9025400>>cheap(close to 1)

According to the calculation below, Since cheap means 1 and expensive means 0, I think Altura would be cheaper than Assagio Ristorante since 0.9025400 is closer to 1, and 1 means cheap!
```{r}

Assagio <- c(Restaurant = "Assagio Ristorante", Food = 23, Decor = 17, Service = 22, East = 0, Cheap = 0)
Altura <- c(Restaurant = "Altura", Food = 18, Decor = 15, Service = 24, East = 1, Cheap = 0)
new_data <- rbind(italian_cheap, Assagio, Altura)
new_data$Food <- as.numeric(new_data$Food)
new_data$Decor <- as.numeric(new_data$Decor)
new_data$Service <- as.numeric(new_data$Service)
new_data$East <- as.numeric(new_data$East)
predicted <- predict(m, newdata = new_data, type = "response")
tail(cbind(new_data, probability = predicted))

```


## Question 3

# Question 3.1
logistic regression:
Who survived in the titanic accident?
(Y) response:0-dies,1-survived
(X) predictors: gender, age, class, status...

linear regression:
How tall is the height of the class?
(Y) response: height(continuous numeric)
(X) predictors: gender, race, weight, food consume per day...

# Question 3.2. 
What does this mean: A coefficient is statistically significant at a 5% confidence level?

When we say something is statistical significant, that means we can reject the H0 null-hypothesis, and prove that H1 is correct. A 5% confidence level means the significance level is 0.05. P-value, the probability density value, which means the possibility of H0 happens, should be very small(<0.05) when it is statistical significant. 
For this situation, P-value with the coefficient is smaller than 0.05. Then we can say the x(predict) variable has relation with the y(response) variable.

# Question 3.3.a
L1
    
| | **Predicted** | |
| -------- | ------------: | ------:|
| | approved users (A) | intruders (I) |
|**Actual**| 3 | 0 |
| | 3 | 4 |


L2

| | **Predicted** | |
| -------- | ------------: | ------:|
| | approved users (A) | intruders (I) |
|**Actual**| 2 | 1 |
| | 0 | 7 |


# Question 3.3.b
L1
accuracy: 3+4/10=0.7
precision:4/4=1
recall:4/(3+4)=0.5714

L2
accuracy:2+7/10=0.9
precision:7/(1+7)=0.875
recall:7/7=1

# Question 3.3.c
I think L2 is a better option.
Because if real intruders be predicted as approved users, it will cause a huge chaos. If network security has any leakage, then it may cause a huge loss for the company or organization and may even cause privacy issues. So it is better to be more careful not to allow any real intruders be predicted as approved users. Also, L2 has better accuracy and recall.
